Report on Certificate Tools

### 2016-08-24 TEX/draft.tex
At least a little bit better code formating, to do from OPENSSL License onward (need to learn how to use citations)

@@

\subsubsection{Viewing stored certificates}
\paragraph{PEM encoded certificates (.pem$|$.cer$|$.crt):}

@@

\paragraph{DER encoded certificates (.der):}

@@

\paragraph{Importing PEM or DER encoded keys or certificates into PKCS#12 file:}

@@

>>>>

\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\} %used for better formating of some text

@@

\subsubsection{Viewing stored certificates}
\myparagraph{PEM encoded certificates (.pem$\vert$.cer$\vert$.crt):}

@@

\myparagraph{DER encoded certificates (.der):}

@@

\myparagraph{Importing PEM or DER encoded keys or certificates into PKCS\#12 file:}

@@

  \subsection{License}
OpenSSL is free to use commercialy, however creating CA is not advised
a) OPENSSL O'REILY page 59 
b) hinted in manual pages.

The ca command is quirky and at times downright unfriendly.

The ca utility was originally meant as an example of how to do things in a CA . It was not supposed to be used as a full blown CA itself: nevertheless some people are using it for this purpose.

The ca command is effectively a single user command: no locking is done on the various files and attempts to run more than one ca command on the same database can have unpredictable results.
